---
title: "ROP Prediction Dashoard"
output: 
  flexdashboard::flex_dashboard:
runtime: shiny

---
<style type="text/css">

.chart-title {
  border-bottom: 1px solid #d7d7d7;
  color: #666;
  font-size: 15px;
  font-weight: 800;
  padding: 7px 10px 4px;
}
</style>

```{r setup, include=FALSE}
require(flexdashboard)
require(dplyr)
require(plotly)
require(ggthemes)
require(ggrepel)


#setwd("~/Ravneet/ROP_visuals")


gg.gauge <- function(pos,breaks, cir_points) {
  pos <- round(pos, 0)
  breaks <- round(breaks, 0)
  require(ggplot2)
  get.poly <- function(a,b,r1=0.5,r2=1.0) {
    th.start <- pi*(1-a/cir_points)
    th.end   <- pi*(1-b/cir_points)
    th       <- seq(th.start,th.end, length = cir_points)
    x        <- c(r1*cos(th),rev(r2*cos(th)))
    y        <- c(r1*sin(th),rev(r2*sin(th)))
    return(data.frame(x,y))
  }
  ggplot()+ 
    geom_polygon(data=get.poly(breaks[1],breaks[2]),aes(x,y),fill="gold")+
    geom_polygon(data=get.poly(breaks[2],breaks[3]),aes(x,y),fill="forestgreen")+
    geom_polygon(data=get.poly(breaks[3],breaks[4]),aes(x,y),fill="red")+
    geom_polygon(data=get.poly(pos-1,pos+1, 0.2),aes(x,y))+
    geom_text(data=as.data.frame(breaks), size=5, fontface="bold", vjust=0.5, hjust =0.75,
              aes(x=1.1*cos(pi*(1-breaks/cir_points)),y=1.1*sin(pi*(1-breaks/cir_points)),label=paste0(breaks)))+
    annotate("text",x=0,y=0,label=pos,vjust=0,size=7,fontface="bold")+
    coord_fixed()+
    theme_bw()+
    theme(axis.text=element_blank(),
          axis.title=element_blank(),
          axis.ticks=element_blank(),
          panel.grid=element_blank(),
          panel.border=element_blank(),
          plot.margin = unit(c(1,1,1,1), "pt")
          ) 
}



bullet.graph <- function(bg.data){
  
  # compute max and half for the ticks and labels
  max.bg <- max(bg.data$high)
  mid.bg <- max.bg / 2

  gg <- ggplot(bg.data) 
  gg <- gg + geom_bar(aes(measure, high, label = high),  fill="forestgreen", stat="identity", width=0.2) 
  gg <- gg + geom_bar(aes(measure, mean, label = mean),  fill="gold", stat="identity", width=0.2) 
  gg <- gg + geom_bar(aes(measure, low, label = low),   fill="red", stat="identity", width=0.2) 
  gg <- gg + geom_bar(aes(measure, value, label = value), fill="black",  stat="identity", width=0.1) 
  #gg <- gg + geom_errorbar(aes(y=target, x=measure, ymin=target, ymax=target), color="red", width=0.45) 
  #gg <- gg + geom_point(aes(measure, target), colour="red", size=2.5) +
  gg <- gg + geom_text(aes(measure, value, label=value, vjust =-0.75, size=8,fontface="bold")) 
  gg <- gg + geom_text(aes(measure, high, label = high, hjust =-0.75, vjust =1, size=8,fontface="bold")) 
  gg <- gg + geom_text(aes(measure, mean, label = mean, hjust =-0.75, vjust =1, size=8,fontface="bold", position = "stack")) 
  gg <- gg + geom_text(aes(measure, low, label = low, hjust =-0.75, vjust =1, size=8,fontface="bold"))
  #gg <- gg + geom_text(position = "stack", hjust =-0.75, size=8,fontface="bold")
  #gg <- gg + scale_y_continuous(breaks=seq(0,max.bg,25), expand = c(0,0))
  gg <- gg + scale_x_discrete(expand=c(0,0))
  gg <- gg + theme_void()+ theme(legend.position="none")
  gg <- gg + ggtitle("Bit Life Estimation")
    #theme_economist()
  #gg <- gg + coord_flip()
  # gg <- gg + theme(axis.text.x=element_blank(),
  #                  axis.title.x=element_blank(),
  #                  axis.line.y=element_blank(),
  #                  axis.line.x=element_blank(),
  #                  axis.text.y=element_text(hjust = -0.1,color="black"),
  #                  axis.ticks.y=element_blank(),
  #                  axis.title.y=element_blank(),
  #                  legend.position="none",
  #                  panel.background=element_blank(),
  #                  panel.border=element_blank(),
  #                  panel.grid.major=element_blank(),
  #                  panel.grid.minor=element_blank(),
  #                  plot.background=element_blank(),
  #                  plot.margin = unit(c(0,0,0,0), "pt"))

  return(gg)

}

df <- read.csv("midtest.csv")
df %>% select(md, formation) %>% group_by(formation) %>% slice(1) -> df_fm_md

# df %>% 
#   select(md,rop,fm_ma100_delta_dep_rop,fm_ma100_delta_dep_rop_for,prediction) %>% 
#   arrange(md) -> df


```

ROP Prediction
=====================================  


Inputs {.sidebar data-width=200}
-----------------------------------------------------------------------
```{r}
sliderInput(inputId = "currentmd", 
            label = "Choose MD range", 
              #value = c(ceiling(df$md[1]/10)*10, floor(df$md[nrow(df)]/10)*10) , min = ceiling(df$md[1]/10)*10, #max = floor(df$md[nrow(df)]/10)*10-100
            min = min(df$md),
            max = max(df$md),
            value = c(min(df$md), max(df$md))
            )
```


```{r}

renderPlot({
    df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]) -> dfii
    bitlife <- dfii$bitlife_est[dfii$md == input$currentmd[2]]
    
    bitlife_df <- data.frame(
                  measure=c("BitLife Estimate"),
                  high=c(100),
                  mean=c(50),
                  low=c(30), 
                  target=c(80),
                  value=c(bitlife)
    )
    
    
    bullet.graph(bitlife_df)
    
  })


```




Column  {data-width=250}
-----------------------------------------------------------------------

### Weight on Bit (klbs)

```{r}


renderPlot({
df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]) -> dfii
wob_val <- dfii$wob[dfii$md == input$currentmd[2]]
lwr_limit <- 0
upr_limit <- 100
opt_lwr <- dfii$wob_lwr[dfii$md == input$currentmd[2]]
opt_upr <- dfii$wob_upr[dfii$md == input$currentmd[2]]
                        
breaks <- c(lwr_limit,opt_lwr, opt_upr, upr_limit)
gg.gauge(wob_val,breaks, 100)
})

```


### Drill-Bit RPM
```{r}

renderPlot({
df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]) -> dfii
dbrpm_val <- dfii$dbrpm0_ma10[dfii$md == input$currentmd[2]]
lwr_limit <- 0
upr_limit <- 500
opt_lwr <- dfii$dbrpm_lwr[dfii$md == input$currentmd[2]]
opt_upr <- dfii$dbrpm_upr[dfii$md == input$currentmd[2]]
                        
breaks <- c(lwr_limit,opt_lwr, opt_upr, upr_limit)
gg.gauge(dbrpm_val,breaks, upr_limit)
})


```

### Flow Rate (gpm)
```{r}

renderPlot({
df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]) -> dfii
flow_val <- dfii$pumpflow[dfii$md == input$currentmd[2]]
lwr_limit <- 0
upr_limit <- 1000
opt_lwr <- dfii$pumpflow_lwr[dfii$md == input$currentmd[2]]
opt_upr <- dfii$pumpflow_upr[dfii$md == input$currentmd[2]]
                        
breaks <- c(lwr_limit,opt_lwr, opt_upr, upr_limit)
gg.gauge(flow_val,breaks, upr_limit)
})


```




Column  {data-width=200}
-----------------------------------------------------------------------

### Weight on Bit (Mean) {.value-box}

```{r}
renderValueBox({

  df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]) -> dfii
  wob_val <- round(mean(dfii$wob, digits = 2))

  valueBox(
    value = wob_val
  )
})

```

### Weight on Bit - Graph 
```{r}


renderPlot({
    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+10) -> dfii
    dfii$wob_ma10[dfii$md > input$currentmd[2]] <- NaN
    dfii$wob_lwr[dfii$md > input$currentmd[2]] <- NaN
    dfii$wob_upr[dfii$md > input$currentmd[2]] <- NaN
    #wob_val <- round(mean(dfii$fm_ma100_delta_dep_wob, digits = 2))

p2=ggplot(data=dfii,aes(x=md)) +
      geom_line(mapping = aes(y = wob_ma10), colour = "red") +
      geom_line(mapping = aes(y = wob_lwr), color = "black", linetype = 2)+
      geom_line(mapping = aes(y = wob_upr), color = "black", linetype = 2)+
      geom_ribbon(aes(ymin = wob_lwr, ymax = wob_upr, fill = formation), alpha = 0.2, linetype = 2, show.legend = FALSE) +
      geom_vline(xintercept = input$currentmd[2])+
      xlab("MD (ft)") +
      ylab("WOB")+
      coord_flip() +
      scale_x_reverse()+
      theme_economist()

p2 #<- ggplotly(p2)

  })
```

Column  {data-width=200}
-----------------------------------------------------------------------

### Drill Bit RPM (Mean) {.value-box}

```{r}
renderValueBox({

  df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]) -> dfii
  dbrpm_val <- round(mean(dfii$dbrpm0_ma10, digits = 2))
  valueBox(
    "Drill Bit RPM (Mean)",
    value = dbrpm_val
  )
})

```

### Drill Bit RPM - Graph 

```{r}

renderPlot({
    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+10) -> dfii
    dfii$dbrpm0_ma10[dfii$md > input$currentmd[2]] <- NaN
    dfii$dbrpm_lwr[dfii$md > input$currentmd[2]] <- NaN
    dfii$dbrpm_upr[dfii$md > input$currentmd[2]] <- NaN

    #df %>% filter(md<=input$startmd+100) -> dfii
    
    p3=ggplot(data=dfii,aes(x=md)) +
      geom_line(mapping = aes(y = dbrpm0_ma10), colour = "red") +
      geom_line(mapping = aes(y = dbrpm_lwr), color = "black", linetype = 2)+
      geom_line(mapping = aes(y = dbrpm_upr), color = "black", linetype = 2)+
      geom_ribbon(aes(ymin = dbrpm_lwr, ymax = dbrpm_upr, fill = formation), alpha = 0.2, linetype = 2, show.legend = FALSE) +
      geom_vline(xintercept = input$currentmd[2])+
      xlab("MD (ft)") +
      ylab("Drill-Bit RPM")+
      coord_flip() +
      scale_x_reverse()+
      theme_economist()

    p3 #<- ggplotly(p3)
    
  })


```

Column  {data-width=200}
-----------------------------------------------------------------------

### Flow Rate (Mean) {.value-box}

```{r}
renderValueBox({

  df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]) -> dfii
  flow_val <- round(mean(dfii$pumpflow_ma10, digits = 2))

  valueBox(
    value = flow_val
  )
})

```

### Flow Rate - Graph 


```{r}

renderPlot({
    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+10) -> dfii
    dfii$pumpflow_ma10[dfii$md > input$currentmd[2]] <- NaN
    dfii$pumpflow_lwr[dfii$md > input$currentmd[2]] <- NaN
    dfii$pumpflow_upr[dfii$md > input$currentmd[2]] <- NaN
    #df %>% filter(md<=input$startmd+100) -> dfii
    
    p3=ggplot(data=dfii,aes(x=md)) +
      geom_line(mapping = aes(y = pumpflow_ma10), colour = "red") +
      geom_line(mapping = aes(y = pumpflow_lwr), color = "black", linetype = 2)+
      geom_line(mapping = aes(y = pumpflow_upr), color = "black", linetype = 2)+
      geom_ribbon(aes(ymin = pumpflow_lwr, ymax = pumpflow_upr, fill = formation), alpha = 0.2, linetype = 2, show.legend = FALSE) +
      #scale_alpha(guide = 'none')+
      geom_vline(xintercept = input$currentmd[2])+
      xlab("MD (ft)") +
      ylab("Flow Rate")+
      coord_flip() +
      scale_x_reverse()+
      theme_economist()

    p3 # <- ggplotly(p3)
    
  })


```

Column {}
-----------------------------------------------------------------------

### Rate of Penetration (Mean) {.value-box}

```{r}
renderValueBox({

  df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+10) -> dfii
  rop_val <- round(mean(dfii$fm_ma10_delta_dep_rop, digits = 2))

  valueBox(
    value = rop_val
  )
})

```

### Rate of Penetration - Prediction vs Actual

```{r}

# currentmd <- reactive(as.numeric(input$currentmd))
# df %>% filter(md>=currentmd & md<=currentmd+500) -> dfii
#     #dfii$rop[401:500] <- NaN
#     dfii$fm_ma100_delta_dep_rop_for[401:500] <- NaN

renderPlot({
    #df %>% filter(md>=input$currentmd & md<=input$currentmd+500) -> dfii
    #df %>% filter(md<=input$currentmd+100) -> dfii
    df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+10) -> dfii
    dfii %>% mutate(lwr = prediction10 - rmse10, upr = prediction10 + rmse10) -> dfii
    
    df_fm_md %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+10) ->df_fm_md_filt
    #levels(dfii$formation)[levels(dfii$formation)=="LAMAR (DELAWARE GP)"] <- "LAMAR-DEL"
    #levels(dfii$formation)[levels(dfii$formation)=="1ST BONE SPRING SAND"] <- "1st BoneSand"
    #levels(dfii$formation)[levels(dfii$formation)=="2ND BONE SPRING LIME"] <- "2nd BoneLime"
    levels(dfii$formation)[levels(dfii$formation)=="2ND BONE SPRING SAND"] <- "2nd BoneSand"
    #levels(dfii$formation)[levels(dfii$formation)=="3RD BONE SPRING LIME"] <- "3rd BoneLime"
    #levels(dfii$formation)[levels(dfii$formation)=="BONE SPRING/AVALON"] <- "Bone Spr/Ava"
    #dfii$rop[401:500] <- NaN
    #dfii$fm_ma100_delta_dep_rop_for[401:500] <- NaN
    dfii$fm_ma10_delta_dep_rop_for[dfii$md > input$currentmd[2]] <- NaN
    # ymin <- min(min(df$fm_ma100_delta_dep_rop_for),min(df$prediction))
    # ymax <- max(max(df$fm_ma100_delta_dep_rop_for),max(df$prediction))
    # ratio.display <- 2/6
    # ratio.values <- (max(df$md)-min(df$md))/(ymax-ymin)
    p1<-ggplot(data=dfii,aes(x=md)) +
      #geom_line(mapping = aes(y = rop), colour = "black") +
      geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "gray30", alpha = 0.2) +
      geom_line(mapping = aes(y = fm_ma10_delta_dep_rop_for, fill = "Actual ROP"), color = "red")+
      geom_line(mapping = aes(y = prediction10, fill = "predicted ROP"), colour = "blue")+
      scale_color_discrete(name = "RunCharts", labels = c("Prediction", "Actual"))+
      geom_rug(sides = "l", aes(color = formation), show.legend = TRUE)+
      scale_color_hue("Formation")+
      scale_fill_manual(
            "Line plots", values=rep(1,2),
            guide=guide_legend(override.aes = list(colour=c("red", "blue")))
      )+
      geom_text_repel(data= df_fm_md_filt, mapping=aes(x=md, y=0, label=formation), size=3, fontface=2) +
      #geom_text(df_fm_md, aes(x = md, y = 0))+
      geom_vline(xintercept = input$currentmd[2])+
      xlab("MD (ft)") +
      ylab("ROP (ft/hr)")+
      coord_flip() +
      scale_x_reverse()+
      theme_economist()+
      theme(legend.direction = "vertical", 
        legend.position = "right"
        )

    
    p1 #<- ggplotly(p1)
    
})

```



BY RUN
===================================== 

Inputs {.sidebar}
-----------------------------------------------------------------------
```{r}
selectInput("run", label = "Run No:",
            choices = c(unique(df$RunNo)), selected = df$RunNo[1])

```


Column {data-width=200}
-----------------------------------------------------------------------

### Weight on Bit
```{r}
#num <- reactive(as.integer(input$run))
renderPlot({
  
    df_run <- df %>% filter(RunNo == input$run)

    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    #df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+100) -> dfii
    #wob_val <- round(mean(dfii$fm_ma100_delta_dep_wob, digits = 2))

  p2=ggplot(data=df_run,aes(x=md)) +
      geom_line(mapping = aes(y = wob_ma10), colour = "red") +
      geom_vline(xintercept = df_run$md[(nrow(df_run)-99)])+
      xlab("MD (ft)") +
      ylab("WOB")+
      coord_flip() +
      scale_x_reverse()

  p2 #<- ggplotly(p2)

  })


```

Column {data-width=200}
-----------------------------------------------------------------------

### Drill String RPM 
```{r}
#num <- reactive(as.integer(input$run))
renderPlot({
  
    df_run <- df %>% filter(RunNo == input$run)

    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    #df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+100) -> dfii
    #wob_val <- round(mean(dfii$fm_ma100_delta_dep_wob, digits = 2))

    p2=ggplot(data=df_run,aes(x=md)) +
      geom_line(mapping = aes(y = dbrpm0_ma10), colour = "red") +
      geom_vline(xintercept = df_run$md[(nrow(df_run)-99)])+
      xlab("MD (ft)") +
      ylab("WOB")+
      coord_flip() +
      scale_x_reverse()

    p2 #<- ggplotly(p2)

  })


```

Column {data-width=200}
-----------------------------------------------------------------------

### Pump Flow Rate 

```{r}
#num <- reactive(as.integer(input$run))
renderPlot({
  
    df_run <- df %>% filter(RunNo == input$run)

    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    #df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+100) -> dfii
    #wob_val <- round(mean(dfii$fm_ma100_delta_dep_wob, digits = 2))

    p2=ggplot(data=df_run,aes(x=md)) +
      geom_line(mapping = aes(y = pumpflow_ma10), colour = "red") +
      geom_vline(xintercept = df_run$md[(nrow(df_run)-99)])+
      xlab("MD (ft)") +
      ylab("WOB")+
      coord_flip() +
      scale_x_reverse()

    p2 #<- ggplotly(p2)

  })


```

Column {data-width=400}
-----------------------------------------------------------------------
### Rate of Penetration - Prediction vs Actual

```{r}

renderPlot({
    
    df_run <- df %>% filter(RunNo == input$run)
    df_run %>% mutate(lwr = prediction10 - 30, upr = prediction10 + 30) -> df_run
    
    #levels(df_run$formation)[levels(df_run$formation)=="LAMAR (DELAWARE GP)"] <- "LAMAR-DEL"
    #levels(df_run$formation)[levels(df_run$formation)=="1ST BONE SPRING SAND"] <- "1st BoneSand"
    #levels(df_run$formation)[levels(df_run$formation)=="2ND BONE SPRING LIME"] <- "2nd BoneLime"
    levels(df_run$formation)[levels(df_run$formation)=="2ND BONE SPRING SAND"] <- "2nd BoneSand"
    #levels(df_run$formation)[levels(df_run$formation)=="3RD BONE SPRING LIME"] <- "3rd BoneLime"
    #levels(df_run$formation)[levels(df_run$formation)=="BONE SPRING/AVALON"] <- "Bone Spr/Ava"
    #df_run$rop[401:500] <- NaN
    
    df_run$fm_ma100_delta_dep_rop_for[(nrow(df_run)-99) : nrow(df_run)] <- NaN
    
    # ymin <- min(min(df$fm_ma100_delta_dep_rop_for),min(df$prediction))
    # ymax <- max(max(df$fm_ma100_delta_dep_rop_for),max(df$prediction))
    # ratio.display <- 2/6
    # ratio.values <- (max(df$md)-min(df$md))/(ymax-ymin)
    p1<-ggplot(data=df_run,aes(x=md)) +
      geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "gray30", alpha = 0.2) +
      geom_line(mapping = aes(y = fm_ma100_delta_dep_rop_for), colour = "red") +
      geom_line(mapping = aes(y = prediction10), colour = "blue") +
      geom_rug(aes(color = formation ))+
      geom_vline(xintercept = df_run$md[(nrow(df_run)-99)])+
      xlab("MD (ft)") +
      ylab("ROP (ft/hr)")+ 
      coord_flip() +
      scale_x_reverse() 
      
    
    p1 #<- ggplotly(p1) 
    
})

```

BY Formation
===================================== 

Inputs {.sidebar}
-----------------------------------------------------------------------
```{r}
selectInput("formation", label = "Choose Formation:",
            choices = c(levels(df$formation)), selected = df$formation[1])

```


Column {data-width=200}
-----------------------------------------------------------------------

### Weight on Bit
```{r}
#num <- reactive(as.integer(input$run))
renderPlot({
  
  df_formation <- df %>% filter(formation == input$formation)

    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    #df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+100) -> dfii
    #wob_val <- round(mean(dfii$fm_ma100_delta_dep_wob, digits = 2))

  p2=ggplot(data=df_formation,aes(x=md)) +
      geom_line(mapping = aes(y = wob_ma10), colour = "red") +
      #geom_line(mapping = aes(y = wob_mean), color = "black")+
      #geom_line(mapping = aes(y = wob_max), color = "black")+
      geom_vline(xintercept = df_formation$md[(nrow(df_formation)-100)])+
      xlab("MD (ft)") +
      ylab("WOB")+
      coord_flip() +
      scale_x_reverse()

  p2 #<- ggplotly(p2)

  })


```

Column {data-width=200}
-----------------------------------------------------------------------

### Drill-Bit RPM 
```{r}
#num <- reactive(as.integer(input$run))
renderPlot({
  
  df_formation <- df %>% filter(formation == input$formation)
   

  p2=ggplot(data=df_formation,aes(x=md)) +
      geom_line(mapping = aes(y = dbrpm0_ma10), colour = "red") +
      geom_vline(xintercept = df_formation$md[(nrow(df_formation)-100)])+
      xlab("MD (ft)") +
      ylab("Drill-Bit RPM")+
      coord_flip() +
      scale_x_reverse()

  p2 #<- ggplotly(p2)

  })


```

Column {data-width=200}
-----------------------------------------------------------------------

### Pump Flow Rate 

```{r}
#num <- reactive(as.integer(input$run))
renderPlot({
  
  df_formation <- df %>% filter(formation == input$formation)

    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    #df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+100) -> dfii
    #wob_val <- round(mean(dfii$fm_ma100_delta_dep_wob, digits = 2))

  p2=ggplot(data=df_formation,aes(x=md)) +
      geom_line(mapping = aes(y = pumpflow_ma10), colour = "red") +
      geom_vline(xintercept = df_formation$md[(nrow(df_formation)-100)])+
      xlab("MD (ft)") +
      ylab("Pumpflow")+
      coord_flip() +
      scale_x_reverse()

  p2 #<- ggplotly(p2)

  })


```

Column {data-width=400}
-----------------------------------------------------------------------
### Rate of Penetration - Prediction vs Actual

```{r}

renderPlot({
    
    df_formation <- df %>% filter(formation == input$formation)
    
    df_formation %>% mutate(lwr = prediction10 - 30, upr = prediction10 + 30) -> df_formation
    
    levels(df_formation$formation)[levels(df_formation$formation)=="LAMAR (DELAWARE GP)"] <- "LAMAR-DEL"
    levels(df_formation$formation)[levels(df_formation$formation)=="1ST BONE SPRING SAND"] <- "1st BoneSand"
    levels(df_formation$formation)[levels(df_formation$formation)=="2ND BONE SPRING LIME"] <- "2nd BoneLime"
    levels(df_formation$formation)[levels(df_formation$formation)=="2ND BONE SPRING SAND"] <- "2nd BoneSand"
    levels(df_formation$formation)[levels(df_formation$formation)=="3RD BONE SPRING LIME"] <- "3rd BoneLime"
    levels(df_formation$formation)[levels(df_formation$formation)=="BONE SPRING/AVALON"] <- "Bone Spr/Ava"
    #df_formation$rop[401:500] <- NaN
    #df_formation$fm_ma100_delta_dep_rop_for[401:500] <- NaN

    df_formation$fm_ma100_delta_dep_rop_for[(nrow(df_formation)-99) : nrow(df_formation)] <- NaN
    # ymin <- min(min(df$fm_ma100_delta_dep_rop_for),min(df$prediction))
    # ymax <- max(max(df$fm_ma100_delta_dep_rop_for),max(df$prediction))
    # ratio.display <- 2/6
    # ratio.values <- (max(df$md)-min(df$md))/(ymax-ymin)
    p1<-ggplot(data=df_formation,aes(x=md)) +
      #geom_line(mapping = aes(y = rop), colour = "black") +
      geom_ribbon(aes(ymin = lwr, ymax = upr), fill = "gray30", alpha = 0.2) +
      geom_line(mapping = aes(y = fm_ma100_delta_dep_rop_for, colour = formation)) +
      geom_line(mapping = aes(y = prediction10), colour = "blue") +
      geom_vline(xintercept = df_formation$md[(nrow(df_formation)-100)])+
      xlab("MD (ft)") +
      ylab("ROP (ft/hr)") +
      coord_flip() +
      scale_x_reverse()+
      geom_rug(sides = "l", aes(color = formation))

    p1
    
    #p1 <- ggplotly(p1)
    
})

```


Column {data-width=200}
-----------------------------------------------------------------------

### Bit Life Estimation 

```{r}

renderPlot({
    #df %>% filter(md>=input$startmd & md<=input$startmd+500) -> dfii
    df %>% filter(md>=input$currentmd[1] & md<=input$currentmd[2]+10) -> dfii
    dfii$bitlife_est[dfii$md > input$currentmd[2]] <- NaN
    #dfii$pumpflow_lwr[dfii$md > input$currentmd[2]] <- NaN
    #dfii$pumpflow_upr[dfii$md > input$currentmd[2]] <- NaN
    #df %>% filter(md<=input$startmd+100) -> dfii
    
    p3=ggplot(data=dfii,aes(x=md)) +
      geom_line(mapping = aes(y = bitlife_est), colour = "red") +
      #geom_line(mapping = aes(y = pumpflow_lwr), color = "black", linetype = 2)+
      #geom_line(mapping = aes(y = pumpflow_upr), color = "black", linetype = 2)+
      #geom_ribbon(aes(ymin = pumpflow_lwr, ymax = pumpflow_upr, fill = formation), alpha = 0.2, linetype = 2, show.legend = FALSE) +
      #scale_alpha(guide = 'none')+
      geom_vline(xintercept = input$currentmd[2])+
      xlab("MD (ft)") +
      ylab("Bit Life Estimation")+
      coord_flip() +
      scale_x_reverse()+
      scale_y_reverse()+
      theme_economist()

    p3 # <- ggplotly(p3)
    
  })


```